Hierarchical Reverberation Mapping

### 2013-12-03 Paper/ms.tex
mu --> m in the context of the AR(1) model

The posterior distribution for the lag $\bar{\tau}$ of a single object
$i$ may be obtained
by fitting the following model. We assume, for simplicity, that
the transfer function is uniform
between limits $a$ and $b$, where $b > a$:
\begin{eqnarray}
\Psi(\tau) &=& \left\{
\begin{array}{lr}
\frac{1}{b-a}, & \tau \in [a,b]\\
0, & \textnormal{otherwise}
\end{array}\right.
\end{eqnarray}
and our goal is to measure the mean lag:
\begin{eqnarray}
\bar{\tau} &=& \int \tau \Psi(\tau) \, d\tau\\
&=& \frac{1}{2}(b-a).
\end{eqnarray}
Note that inferring $\bar{\tau}$ from the data requires that we
marginalise over an infinite number of nuisance parameters describing the
behaviour of $y(t)$ at unobserved times \citep{pancoast}.
The prior for the underlying time variation of the continuum emission is
a continuous autoregressive process of order 1, or a CAR(1) model. These models
have been studied extensively for AGN variability
\citep[e.g.][]{2009ApJ...698..895K, 2011ApJ...735...80Z, 2013ApJ...765..106Z}.
This marginalisation can be done
either analytically or inside MCMC. We used the latter approach for simplicity.
We discretised
time using ten time bins per day, and have a discrete continuum light curve
$\mathbf{y} = \{y_1, ..., y_n\}$, included in the model as a set of unknown
parameters. The prior for these parameters is:
\begin{eqnarray}
p(y_i | y_{i-1},  \mu, a, \beta) \sim \mathcal{N}
\left(\mu + a\left(y_{i-1} - \mu\right), \beta^2\right)
\end{eqnarray}
for $i \geq 2$. This is the discrete AR(1) model from time series theory.
$\mu$ describes the mean level of the continuum light curve, $\beta$ controls
the size of the short-term fluctuations, and $a$ controls the correlation
timescale (the timescale is given by $L = -1/\ln(a)$).

@@

We used vague priors for the parameters of the single-object model. In practice
these could be made substantially narrower.
We chose a log-uniform prior for $L$ (the AGN variability timescale)
between $0.1$ and $10^5$ days, a log-uniform
prior for $\beta$ (the size of the short-term fluctuations)
between $10^{-3}$ and $10^3$ flux units, a Cauchy(0, 100)
prior for $\mu$ (the mean flux level of the AGN), a log-uniform prior for $b$
(the upper limit of the transfer function) between $10^{-4}$ and $10^2$ days,
a uniform prior for $a$ (the lower limit of the transfer function)
between 0 and $b$, a log-uniform prior between
$10^{-3}$ and $10^3$ for the response coefficient $A$ and a Cauchy(0, 100) prior
for the second response parameter $C$.

>>>>

The posterior distribution for the lag $\bar{\tau}$ of a single object
$i$ may be obtained
by fitting the following model. We assume, for simplicity, that
the transfer function is uniform
between limits $a$ and $b$, where $b > a$:
\begin{eqnarray}
\Psi(\tau) &=& \left\{
\begin{array}{lr}
\frac{1}{b-a}, & \tau \in [a,b]\\
0, & \textnormal{otherwise}
\end{array}\right.
\end{eqnarray}
and our goal is to measure the mean lag:
\begin{eqnarray}
\bar{\tau} &=& \int \tau \Psi(\tau) \, d\tau\\
&=& \frac{1}{2}(b-a).
\end{eqnarray}
Note that inferring $\bar{\tau}$ from the data requires that we
marginalise over an infinite number of nuisance parameters describing the
behaviour of $y(t)$ at unobserved times \citep{pancoast}.
The prior for the underlying time variation of the continuum emission is
a continuous autoregressive process of order 1, or a CAR(1) model. These models
have been studied extensively for AGN variability
\citep[e.g.][]{2009ApJ...698..895K, 2011ApJ...735...80Z, 2013ApJ...765..106Z}.
This marginalisation can be done
either analytically or inside MCMC. We used the latter approach for simplicity.
We discretised
time using ten time bins per day, and have a discrete continuum light curve
$\mathbf{y} = \{y_1, ..., y_n\}$, included in the model as a set of unknown
parameters. The prior for these parameters is:
\begin{eqnarray}
p(y_i | y_{i-1},  m, a, \beta) \sim \mathcal{N}
\left(m + a\left(y_{i-1} - m\right), \beta^2\right)
\end{eqnarray}
for $i \geq 2$. This is the discrete AR(1) model from time series theory.
$m$ describes the mean level of the continuum light curve, $\beta$ controls
the size of the short-term fluctuations, and $a$ controls the correlation
timescale (the timescale is given by $L = -1/\ln(a)$).

@@

We used vague priors for the parameters of the single-object model. In practice
these could be made substantially narrower.
We chose a log-uniform prior for $L$ (the AGN variability timescale)
between $0.1$ and $10^5$ days, a log-uniform
prior for $\beta$ (the size of the short-term fluctuations)
between $10^{-3}$ and $10^3$ flux units, a Cauchy(0, 100)
prior for $m$ (the mean flux level of the AGN), a log-uniform prior for $b$
(the upper limit of the transfer function) between $10^{-4}$ and $10^2$ days,
a uniform prior for $a$ (the lower limit of the transfer function)
between 0 and $b$, a log-uniform prior between
$10^{-3}$ and $10^3$ for the response coefficient $A$ and a Cauchy(0, 100) prior
for the second response parameter $C$.
